\documentclass[11pt]{article}

% --- Packages ---
\usepackage{amsmath,amssymb}    % math symbols
\usepackage{graphicx}           % figures
\usepackage{array}              % tables
\usepackage{booktabs}           % better tables
\usepackage{geometry}           % page layout
\usepackage{natbib}             % bibliography
\usepackage{hyperref}           % clickable links
\hypersetup{
    colorlinks=true,
    linkcolor=cyan,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
}
\geometry{a4paper, margin=1in}

\title{The CAPIBARA Collaboration}

\author{
    Joan Alcaide-Núñez\thanks{Ludwig-Maximilians-Universität München (LMU), Munich, Germany} \and
    Lluc Soler Manich\thanks{Universitat Politècnica de Catalunya (UPC), Barcelona, Spain} \and
    Alessandro Sabia \and
    Martina Solano Soto \and
    Rosa Bermejo Sabugo\thanks{Universidad de Salamanca (USal), Salamanca, Spain} \and
    Hongda Zheng Xu \and
    Carles Fonseca Maurí\thanks{University of California - Los Angeles, Los Angeles, USA}
}

\date{\today}

\begin{document}

\maketitle

\begin{abstract}

The world of astrophysics is constantly in evolution. The detection of the first gravitational-wave signal 10 years ago opened a new way of detecting the universe, making many open questions regarding the behaviour of gravity and high-energy, compact objects possible to investigate. The Collaboration for the Analysis of Photonic and Ionic Bursts and RAdiation (CAPIBARA Collaboration) is a group of ambitious young students (from high school to university) proposing and working on two projects to observe this side of the cosmos. Our Cosmic Ray Detector project and the COSMOS programme presented in this paper serve not only scientific objects but also have a major education impact.

\end{abstract}

\textbf{Keywords:} Student CubeSat Missions, Multi-Messenger Astronomy, Cosmic Rays

\section{Introduction}

The landscape of modern space exploration is shifting toward more inclusive, decentralised models, where student-led missions play vital roles in both technical innovation and the cultivation of the next generation of space professionals. The rise of CubeSats over the past decade has democratized space access, enabling students to gain early experience in space engineering and fostering new talents. For instance, 14 CubeSats have been launched by European students through ESA's FlyYourSatellite! Programme \cite{missing}, demonstrating the viability of student-developed space hardware.

The Collaboration for the Analysis of Photonic and Ionic Bursts And RAdiation (CAPIBARA Collaboration) is an international student-led initiative founded in summer 2024 with the goal of exploring the high-energy universe. Our members are high school and undergraduate students, creating a unique educational environment where participants can test their interests and skills while contributing to the project. With students at the centre, we are seeking advisors across academia and industry to provide informal mentorship and guidance.

Our scientific focus is high-energy astrophysics, motivated by the upcoming "era of multi-messenger astronomy" \cite{missing}. The August 2017 detection of GW170817 demonstrated the transformative potential of coordinated gravitational wave and electromagnetic observations \cite{missing}. Next-generation facilities like Einstein Telescope and LISA will detect hundreds to thousands of gravitational wave events annually, creating unprecedented demand for rapid electromagnetic counterpart identification. Current high-energy monitoring capabilities rely on aging assets like \textit{Fermi} and \textit{Swift}, with a critical observational gap emerging in the early 2030s.

To address both this scientific need and our educational mission, CAPIBARA pursues two complementary programs: a Cosmic Ray Detector (CRD) for particle physics, and the Constellation of Student-Made Observing CubeSats (COSMOS) for space-based transient astronomy. This dual approach allows students to progress from simpler instrumentation to increasingly complex space missions, building expertise incrementally while maximizing scientific impact.

\section{Cosmic Ray Detector}

The goal of the Cosmic Ray Detector (CAPICR) is to detect and study the flux and energy spectrum of primary cosmic rays (CRs): charged, highly energetic particles with relativistic speeds coming from outer space or the Sun. These rays get blocked by Earth’s atmosphere, therefore to overcome this limitation we aim to insert our CR detector into orbit. 

An ambitious goal that we plan to achive thanks to the partnership with OBA Space, which will deploy our CubeSat as a payload on OAB FARADAY.

Given that the detector will be hosted in a CubeSat, we have optimised it for a small space. It consists of a 60 mm cube that has three compartments. The top one will host the plastic scintillator, which is connected to the silicon photomultiplier (SiPM), the central compartment will hold the electrical circuit. Lastly, in the bottom compartment, we will keep the batteries and the memory storage needed.

When a charged particle passes through the scintillator, its atoms are excited; as they return to the normal state, some photons are emitted. The photons will then be collected by a Silicon Photomultiplier (SiPM), which will transform the collection into a peak of voltage to allow us to detect the event. We do not have any control over the direction of photons emitted by the scintillator; therefore, we need to redirect them to the SiPM, by making the chamber fully reflective, we allow the photons to bounce off the walls until they get collected by it. To achive this the detector will be built of metal (likely aluminium)

Initially, the detector will focus on photon count, i.e., we won’t address the energy or the charge of the CRs yet. This helps us to understand how different orientations affect the CR ratio of detection. Moreover, we intend to send two identical detectors, which will be aligned with some separation between them. This will allow us to better determine the direction from which the CRs come and the speed at which these CRs travel, as we will know the distance between detectors and the difference in detection time.  %how will we mesure this time difference ? 

Currently we are working on the detector 3D model %something more to add?
with guidance and technical support from PLD Space's SPARK program along side OBA Space.

\section{Constellation of Student-Made Observing CubeSats (COSMOS)}

The COSMOS program represents CAPIBARA's long-term strategic vision, aiming to bridge a critical observational gap in high-energy astrophysics throughout the 2030s. The scientific rationale centers on detecting and rapidly localizing high-energy transient events—particularly gamma-ray bursts (GRBs) and electromagnetic counterparts to gravitational wave sources.

\subsection*{Scientific Motivation}

Next-generation gravitational wave observatories (Einstein Telescope, LISA, Cosmic Explorer) will detect hundreds to thousands of events annually, but localizing these sources requires electromagnetic counterparts. High-energy transients like GRBs provide crucial early detection, as they begin with brief gamma-ray/X-ray emission before evolving to longer wavelengths. Rapid, precise localization enables follow-up observations for host galaxy identification (essential for redshift measurements), jet physics studies, and multi-messenger correlation.

Current capabilities face a coverage gap: \textit{Swift} and \textit{Fermi} are aging, and while missions like SVOM and HERMES provide some coverage, no existing or firmly planned mission combines continuous all-sky monitoring with arcminute-level localization and a scalable, sustainable architecture for the 2030s.

\subsection*{Phased Mission Architecture}

COSMOS follows a three-phase development strategy. \textbf{Phase 0 (2024-2026)} focuses on collaboration infrastructure, field study, and documentation, culminating in our SSEA 2026 presentation and Mission Concept Document. \textbf{Phase 1: COSMOS-Twin (2026-2032)} deploys two 3-6U CubeSats to demonstrate time-delay localization. Using GPS-synchronized clocks ($\sim$100 ns accuracy), the satellites detect the same transient and compare arrival times to constrain source position along a hyperbolic region on the celestial sphere. Twin will measure $\sim$10 bright GRBs, validating the localization technique and building flight experience. Launch is planned via ESA's FYS! program or commercial rideshare.

\textbf{Phase 2: COSMOS-Net (2031-2040)} scales to 6-8 satellites in constellation, enabling true triangulation for arcminute-level localization. With three or more satellites detecting an event, time-delay measurements yield precise sky coordinates. The modular design allows satellites to be replaced as they age, ensuring sustained operations. COSMOS-Net will integrate into the broader multi-messenger alert network (GCN), providing rapid public alerts for community follow-up.

\subsection*{Technical Approach}

COSMOS leverages flight-proven detector technology from EIRSAT-1, GRBAlpha, HERMES, and BurstCube, using CsI or GAGG(Ce) scintillators with SiPM or CZT readout covering 10-2000 keV. By building on existing heritage rather than developing novel detectors, we reduce risk and focus innovation on constellation coordination, autonomous transient recognition, and time-delay localization algorithms. The identical-satellite approach for Twin halves design burden and enables cross-validation.

Key technical challenges include GPS-based timekeeping for precise synchronization, onboard trigger algorithms, inter-satellite communication for rapid cross-validation, and constellation orbit maintenance. Our Advisory Board provides structured mentorship to address these challenges, making COSMOS a valuable training ground for future space professionals while delivering scientifically meaningful data.


\section{Discussion}

The two-mission approach provides a structured pathway for technical capability building. The CRD validates core detector and data acquisition technologies at ground level. COSMOS-Twin then demonstrates time-delay localization and constellation operations using two satellites, targeting ~10 bright GRBs to measure localization precision versus baseline distance.

COSMOS-Net's role is providing continuous all-sky monitoring during the 2030s era of advanced gravitational wave observatories. This generates a systematic sample of high-energy transients, enabling multi-messenger correlation studies currently impossible with fragmented existing capabilities. The modular design allows incremental deployment and technology evolution as satellites age, supporting a 15-year operational timeline across distributed university partnerships.

\section{Conclusion}\label{sec:conclusion}

CAPIBARA pursues two complementary missions to address the high-energy observational gap in the 2030s: the CRD validates detector technologies; COSMOS-Twin demonstrates time-delay localization; COSMOS-Net provides systematic transient monitoring paired with Einstein Telescope and LISA operations. Implementation leverages proven detector heritage from EIRSAT-1, GRBAlpha, HERMES, and BurstCube through distributed university partnerships.

Key milestones include CRD completion (2026), COSMOS-Twin launch (2030), and COSMOS-Net deployment (2033-2035). Success requires sustained collaboration, timely funding, and reliable launch access.

\section*{Acknowledgments}

We are grateful to the members of the CAPIBARA Collaboration for useful discussions and feedback. The authors are happy to welcome feedback and advice, please contact the corresponding author or visit our website: \href{https://capibara3.github.io/contact}{capibara3.github.io/contact}.

% We thank the developers of the open-source tools used in this work. 

% --- References ---
% \bibliographystyle{plain}
\bibliographystyle{unsrt}
\bibliography{references}


\end{document}
